Analysis of HTTPS Adoption and Third-party Tracking: \\A Swedish Perspective

### 2015-05-02 paper/figures.tex
Restore deleted figures

\nextgroupplot[
	title=(c) Resource security,
	allDatasetsStackedXbar,
	allDatasetsXbar,
	allDatasetsXbarMiniResults,
	yticklabels={alexa.top.10k-hw,alexa.top.10k-sw,alexa.top.se-hw,alexa.top.se-sw,se.r.100k-hw,se.r.100k-sw,se.hs.municip-hw,se.hs.municip-sw},
]

@@

>>>>

\nextgroupplot[
	title=(c) Resource security,
	allDatasetsStackedXbar,
	allDatasetsXbar,
	allDatasetsXbarMiniResults,
	yticklabels={Top 10k global,Top 10k global (HTTPS), Top 10k .se,Top 10k .se (HTTPS),Rand 100k .se,Rand 100k .se (HTTPS),Municipal .se,Municipal .se (HTTPS)},
]

@@

\begin{tikzpicture}
\begin{axis}[
	% title=(a) Internal resources,
	datasetsCDF,
	datasetsCDFMiniResults,
	xlabel=Ratio of internal resources,
	ylabel=Ratio of domains,
	legend style={at={(1.025,.5)}, anchor=west},
]

	\legend{Top 10k global,Top 10k global (HTTPS), Top 10k .se,Top 10k .se (HTTPS),Rand 100k .se,Rand 100k .se (HTTPS),Municipal .se,Municipal .se (HTTPS)},
